Model Samples Processing

### 2020-01-24 stats/model.Rmd
prep model for long run

global_sigma <- readRDS("../saves/global_sigma.rds")

#### summaries
item_params_summary <- item_params %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary <- global_params %>%
  group_by (parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

@@

```{r}
plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~item, scales = 'free')+
  theme_few()

@@

plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type~parameter, scales = 'free')+
  theme_few()

@@

```{r}
plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(type~parameter, scales = 'free')+
  theme_few()

plot_global_sigma
```

```{r}
plotg_subj_sigma <- ggplot(subj_sigma, aes(x = sigma, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Subject Sigma")+
  theme_few()

@@

plot_model_pred <- model_pred%>%
  group_by(model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol()+
  scale_fill_ptol()

@@

cor_prag <- model_pred%>%
  filter(model == "pragmatic")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

@@

cor_model_pred <- bind_rows(
  cor_prag,
  cor_global,
  cor_flat,
  cor_prior
)

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      binnned_data%>%mutate(model = "pragmatic"),
      binnned_data%>%mutate(model = "global"),
      binnned_data%>%mutate(model = "flat"),
      binnned_data%>%mutate(model = "prior")
      )
  )

@@

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(model~age)+
  theme_few() + 
  scale_colour_ptol(name ="Alignment")
```

>>>>

item_sigma <- readRDS("../saves/item_sigma.rds")

subject_sigma <- readRDS("../saves/subject_sigma_re.rds")

item_params <- bind_rows(
  readRDS("../saves/item_params.rds")%>%mutate(run = "no re"),
  readRDS("../saves/item_params_re.rds")%>%mutate(run = "re")
)

global_params <- bind_rows(
  readRDS("../saves/global_params.rds")%>%mutate(run = "no re"),
  readRDS("../saves/global_params_re.rds")%>%mutate(run = "re")
)

item_sigma <- bind_rows(
  readRDS("../saves/item_sigmas.rds")%>%mutate(run = "no re"),
  readRDS("../saves/item_sigma_re.rds")%>%mutate(run = "re")
)

model_pred <- bind_rows(
    readRDS("../saves/model_pred.rds")%>%mutate(run = "no re")%>%filter(model == "pragmatic"),
    readRDS("../saves/model_pred_re.rds")%>%mutate(run = "re")%>%filter(model == "pragmatic")
)

#### summaries
item_params_summary <- item_params %>%
  group_by(run, item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params_summary <- global_params %>%
  group_by (run,parameter,type)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

subject_sigma_summary <- subject_sigma %>%
  group_by (parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

@@

```{r}
plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(run ~parameter + item, scales = 'free')+
  theme_few()

@@

plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(run~type + parameter, scales = 'free')+
  theme_few()

@@

```{r}
plot_item_sigma <- ggplot(item_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(run ~type + parameter, scales = 'free')+
  theme_few()

plot_item_sigma
```

```{r}
plotg_subj_sigma <- ggplot(subject_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Subject Sigma")+
  theme_few()

@@

plot_model_pred <- model_pred%>%
  filter(model == "pragmatic")%>%
  group_by(run, model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = run), size = 1)+
  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = run), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol()+
  scale_fill_ptol()

@@

cor_prag <- model_pred%>%
  filter(model == "pragmatic",
         run == "no re")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(run, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_prag_re <- model_pred%>%
  filter(model == "pragmatic",
         run == "re")%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(run, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

@@

cor_model_pred <- bind_rows(
  cor_prag,
  cor_prag_re,
  #cor_global,
  #cor_flat,
  #cor_prior
)

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      binnned_data%>%mutate(run = "no re"),
      binnned_data%>%mutate(run = "re"),
      # binnned_data%>%mutate(model = "flat"),
      # binnned_data%>%mutate(model = "prior")
      )
  )

@@

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(run~age)+
  theme_few() + 
  scale_colour_ptol(name ="Alignment")
```

### 2020-01-24 stats/model_sample_processing.Rmd
prep model for long run

model <- bind_rows(
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-10_burn0_lag0_chain1.csv")%>%mutate(chain = 1)
)

>>>>

model <- bind_rows(
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2),
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain3.csv")%>%mutate(chain = 3),
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain4.csv")%>%mutate(chain = 4),
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain4.csv")%>%mutate(chain = 5),
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain4.csv")%>%mutate(chain = 6)
)
